Constraining speed of gravitational wave and Newton's constant in binary systems

### 2022-12-20 paper.tex
abstract

\documentclass{article}
\usepackage{amsmath}
\def\d{\mathrm{d}}
\def\p{\partial}
\title{Constraining speed of gravitational wave and Newton's constant in binary systems}
\author{An Jiachen}
\begin{document}

@@

@@

\section{Conclusion}
In this paper, we provided a method to constrain speed of GW $c$ and Newton's constant $G$ in binary systems by comparing the results, which are obtained by using GW and EMW observation data and methods in former researches, of measuring the luminosity distances of the binary systems. This method can be practicable when \eqref{lorentz} and \eqref{maxwell} are vaild, together with:
\begin{enumerate}
    \item the speeds of two components of binary are low;
    \item in a spherical region where binary is located at the center, $c$ and $G$ are nearly constants, and the radius of the region is much greater than the distance between two components of binary;
    \item both $c$ and $G$ are only related to $r$, the distance from binary;
    \item $\frac{\d}{\d r}\ln c$, $\frac{\d}{\d r}\ln G$, $\frac{\d^2}{\d r^2}\ln c$, $\frac{\d^2}{\d r^2}\ln G$ are all small.
\end{enumerate}
The strength of constraining $c$ and $G$ by using method provided in this paper is depended on the uncertainties of the results of measuring the luminosity distances of the binary systems, especially that by using GW observation data. Therefore, to strongly constrain $c$ and $G$, results of using GW observation data to constrain the luminosity distances of the binary systems in unreached high precision are needed.

>>>>

\documentclass{article}
\usepackage{amsmath}
\def\d{\mathrm{d}}
\def\p{\partial}
\title{Constraining speed of gravitational wave and Newton's constant in binary systems}
\author{An Jiachen}
\date{}
\begin{document}

@@

\begin{abstract}
    Any constant varying in space and/or time will induce a violation of the universality of free fall. In this paper we provided a method to constrain speed of gravitational wave and Newton's constant in binary systems by comparing the results, which are obtained by using gravitational wave and electromagnetic wave observation data and methods in former researches, of measuring the luminosity distances of the binary systems. To strongly constrain speed of gravitational wave and Newton's constant by using method provided in this paper, results of using gravitational wave observation data to measure the luminosity distances in unreached high precision are needed.
\end{abstract}

@@

\section{Conclusion}
In this paper, we provided a method to constrain speed of GW $c$ and Newton's constant $G$ in binary systems by comparing the results, which are obtained by using GW and EMW observation data and methods in former researches, of measuring the luminosity distances of the binary systems. This method can be practicable when \eqref{lorentz} and \eqref{maxwell} are vaild, together with:
\begin{enumerate}
    \item the speeds of two components of binary are low;
    \item in a spherical region where binary is located at the center, $c$ and $G$ are nearly constants, and the radius of the region is much greater than the distance between two components of binary;
    \item both $c$ and $G$ are only related to $r$, the distance from binary;
    \item $\frac{\d}{\d r}\ln c$, $\frac{\d}{\d r}\ln G$, $\frac{\d^2}{\d r^2}\ln c$, $\frac{\d^2}{\d r^2}\ln G$ are all small.
\end{enumerate}
The strength of constraining $c$ and $G$ by using method provided in this paper is depended on the uncertainties of the results of measuring the luminosity distances, especially that by using GW observation data. Therefore, to strongly constrain $c$ and $G$, results of using GW observation data to measure the luminosity distances in unreached high precision are needed.
